\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-15 article.tex
wording in the filtering part

% Defects of the imaging device
and will have to cope with
a slower sampling rate than the neuron firing speed, a superposition
of the activity of several neurons and the slow decay of fluorescent calcium
indicator.

>>>>

% Defects of the imaging device
% and will have to cope with
% a slower sampling rate than the neuron firing speed, a superposition
% of the activity of several neurons and the slow decay of fluorescent calcium
% indicator.

The raw signal is the calcium fluorescence imaging representing neuron activity. Considering the imaging process, we have to cope with a slower sampling rate than the neuron firing frequency and the slow decay of fluorescent calcium indicator after a neuron activity burst.
